Thank you, next: partner turnover elevates benefits of mutualism for an ant-tended plant

### 2024-01-16 Manuscript/References_Cacti.tex
Updates

>>>>

@article{Wetzel2023,
	abstract = {Plants and herbivores are remarkably variable in space and time, and variability has been considered a defining feature of their interactions. Empirical research, however, has traditionally focused on understanding differences in means and overlooked the theoretically significant ecological and evolutionary roles of variability itself. We review the literature with the goal of showing how variability-explicit research expands our perspective on plant-herbivore ecology and evolution. We first clarify terminology for describing variation and then review patterns, causes, and consequences of variation in herbivory across scales of space, time, and biological organization. We consider how incorporating variability improves existing hypotheses and leads to new ones. We conclude by suggesting future work that reports full distributions, integrates effects of variation across scales, describes nonlin-earities, and considers how stochastic and deterministic variation combine to determine herbivory distributions. 451},
	author = {William C Wetzel and Brian D Inouye and Philip G Hahn and Susan R Whitehead and Nora Underwood},
	doi = {10.1146/annurev-ecolsys-102221},
	journal = {Annu. Rev. Ecol. Evol. Syst. 2023},
	keywords = {defense,ecological variability,herbivore,herbivory,plant,species interactions},
	pages = {2023},
	title = {Annual Review of Ecology, Evolution, and Systematics Variability in Plant-Herbivore Interactions},
	volume = {54},
	url = {https://doi.org/10.1146/annurev-ecolsys-102221-},
	year = {2023},
